### 2022-07-22 sections/data_presel.tex
update to atlaslatex-13.5.0

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers that have a looser identification criterion and no isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016--2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-$\tau$ triggers, the $\pt$ threshold for the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt that is at least 1~\GeV\ above the threshold. 
The reconstructed $\tau$-leptons are required to have a \pt at least 5~\GeV\ higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channels are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. Requirements are placed on the following additional quantities.
%Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: To enhance selection of the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay, exactly one $\had$ with opposite-sign charge to $\lep$ is required, plus at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: To enhance selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay, exactly one light lepton and two opposite-sign $\had$ are required,
  plus jets with exactly one $b$-jet.
\item $t_{\ell}\had$: This channel enhances the selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the applied reconstruction or identification
  criterion so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the final states used in other ATLAS searches, exactly one $\had$ with the same charge as that assigned to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}

>>>>

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers that have a looser identification criterion and no isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016--2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-$\tau$ triggers, the $\pt$ threshold for the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt that is at least 1~\GeV\ above the threshold. 
The reconstructed $\tau$-leptons are required to have a \pt at least 5~\GeV\ higher than the trigger threshold.
%and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channels are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. The following additional requirements are applied.
%Requirements are placed on the following additional quantities.
%Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: To enhance selection of the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay, exactly one $\had$ with opposite-sign charge to $\lep$ is required, plus at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: To enhance selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay, exactly one light lepton and two opposite-sign $\had$ are required,
  plus jets with exactly one $b$-jet.
\item $t_{\ell}\had$: This channel enhances the selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the applied reconstruction or identification
  criterion so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the final states used in other ATLAS searches, exactly one $\had$ with the same charge as that assigned to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}

### 2022-07-22 sections/objects.tex
update to atlaslatex-13.5.0

Muon candidates~\cite{MUON-2018-03} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are re-fitted using the complete track information from both detector systems.
Muon candidates are required to satisfy `medium' identification criteria~\cite{Aad:2016jkr}.

@@

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from calorimeter energy clusters and
associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
%~\cite{ATL-PHYS-PUB-2015-045}.
Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$.
%Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A recurrent neural network (RNN)~\cite{Graves:2012SCI}
%~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
%A. Graves, Supervised Sequence Labelling with Recurrent Neural Networks, Studies in Computational Intelligence 385, Springer, 2012.
using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
Three working points, labelled `loose', `medium' and `tight', are defined and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the `medium'
working point for the $\had$ selection.
%, while the loose working point is used for background estimation.
The `medium' working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
decays, and an expected rejection factor of 35 (240) against light jets~\cite{ATL-PHYS-PUB-2019-033}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Events are rejected if the jet seeding the $\had$ candidate is $b$-tagged.
%Events with a $b$-tagged  $\had$ candidate are rejected.
%(TBD: check RNN description and update then numbers)
%Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
%$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
%within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
%and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
%In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
%is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
%In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
%candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
%analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.

>>>>

Muon candidates~\cite{MUON-2018-03} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are re-fitted using the complete track information from both detector systems.
Muon candidates are required to have $|\eta|<2.5$, and to satisfy `medium' identification criteria~\cite{Aad:2016jkr}.

@@

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from calorimeter energy clusters and
associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
%~\cite{ATL-PHYS-PUB-2015-045}.
Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$, and to have $\pt>25$ GeV with $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A recurrent neural network (RNN)~\cite{Graves:2012SCI}
%~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
%A. Graves, Supervised Sequence Labelling with Recurrent Neural Networks, Studies in Computational Intelligence 385, Springer, 2012.
using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
Three working points, labelled `loose', `medium' and `tight', are defined and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the `medium'
working point for the $\had$ selection.
%, while the loose working point is used for background estimation.
The `medium' working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
decays, and an expected rejection factor of 35 (240) against light jets~\cite{ATL-PHYS-PUB-2019-033}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Events are rejected if the jet seeding the $\had$ candidate is $b$-tagged.
%Events with a $b$-tagged  $\had$ candidate are rejected.
%(TBD: check RNN description and update then numbers)
%Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
%$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
%within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
%and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
%In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
%is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
%In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
%candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
%analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.

### 2022-07-22 sections/statistical_analysis.tex
update to atlaslatex-13.5.0

The fitting procedure was initially validated through extensive studies using pseudo-data (which is defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminating variable with 
a signal contamination above 10\% are excluded (referred to as `blinding' requirements).
In both cases, the robustness of the model with respect to systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to determine the strength of a simulated signal injected into the real data.

>>>>

The fitting procedure was initially validated through extensive studies using pseudo-data (which is defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminating variable with 
an expected signal contamination above 10\%, assuming $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$, are excluded (referred to as `blinding' requirements).
In both cases, the robustness of the model with respect to systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to determine the strength of a simulated signal injected into the real data.
